Project for the R programming section 
========================================================

***

### Read data 

```{r Get data}
ch <- read.csv("C:/Users/BELHABICH/Desktop/Yacine/1 Entrepreunariat/1 Analytics Business Consulting/5 Training/1 Tech leaders AAL/1 Udacity Support/2 R PROGRAMMING/5 Project/chicago.csv")

ny <- read.csv("C:/Users/BELHABICH/Desktop/Yacine/1 Entrepreunariat/1 Analytics Business Consulting/5 Training/1 Tech leaders AAL/1 Udacity Support/2 R PROGRAMMING/5 Project/new-york-city.csv")

wash <- read.csv("C:/Users/BELHABICH/Desktop/Yacine/1 Entrepreunariat/1 Analytics Business Consulting/5 Training/1 Tech leaders AAL/1 Udacity Support/2 R PROGRAMMING/5 Project/washington.csv")
```

# Load packages 
```{r Packages}
library(tidyverse)
```


# Discovering chicago data
```{r }
glimpse(ch)
names(ch) 
```


```{r }
glimpse(ny)
names(ny) 
```
***

```{r }
glimpse(wash)
names(wash) 
```

***
```{r }
names(ny)
```

```{r }
names(wash)
```

```{r }
names(ch)
```


#1 Popular times of travel (i.e., occurs most often in the start time)

    
***
```{r }
ny3 <- ny2 %>% 
  group_by(Gender) %>%
  summarise(Average_duration = round(mean(Trip.Duration), 2), 
            Media_duration = round(median(Trip.Duration), 2), 
            SD_duration = round(sd(Trip.Duration), 2)
            ) 
ny3

```

***

```{r }
ggplot(ny2, aes(x = Trip.Duration)) + 
xlim(0, 3500) + 
geom_density()+ 
ggtitle("Male-Female comparaison according to trip duration") + 
labs(x = "Trip duration", y = "Trip duration's Density")+
facet_wrap(~Gender ) 

```



```{r }
chi3 <- chi2 %>% 
  group_by(Gender) %>%
  summarise(Average_duration = round(mean(Trip.Duration), 2), 
            Media_duration = round(median(Trip.Duration), 2), 
            SD_duration = round(sd(Trip.Duration), 2)
            ) 
chi3
```



```{r }
ggplot(chi2, aes(x = Trip.Duration)) + 
xlim(0, 3500) + 
geom_density()+ 
ggtitle("Male-Female comparaison according to trip duration") + 
labs(x = "Trip duration", y = "Trip duration's Density")+
facet_wrap(~Gender ) 
```


```{r }
library(tidyverse)

```



    What is the most common day of week?
    What is the most common hour of day?

#2 Popular stations and trip

    What is the most common start station?
    What is the most common end station?
    What is the most common trip from start to end (i.e., most frequent combination of start station and end station)?

#3 Trip duration

    What is the total travel time for users in different cities?
    What is the average travel time for users in different cities?

#4 User info

    What are the counts of each user type?
    What are the counts of each gender (only available for NYC and Chicago)?
    What are the earliest, most recent, most common year of birth (only available for NYC and Chicago)?


***
```{r Scatterplots}

```

***

***
```{r Scatterplots}

```

***

***
```{r Scatterplots}

```

***

***
```{r Scatterplots}

```

***

***
```{r Scatterplots}

```

***